\section{Bounded interfaces and no-ladder obstructions}\label{sec:bounded-interface}

This section isolates two finite obstructions to indefinite refinement under audited closure.
The first is a simple idempotence observation. The second is a counting argument: under a fixed
deterministic interface, there are only finitely many definable predicates, hence no infinite strictly
increasing ladder of distinct definable distinctions.

\subsection{Idempotent saturation}

Let $\X$ be a finite set and let $e:\X\to\X$ be a deterministic packaging operator.
For an integer $n\ge 1$, write $e^{\circ n}$ for the $n$-fold iterate
$e^{\circ n} = \underbrace{e\circ\cdots\circ e}_{n\ \text{times}}$.

\begin{lemma}\label{lem:idempotent-iterates}
If $e\circ e = e$, then $e^{\circ n}=e$ for all integers $n\ge 1$.
\end{lemma}

\begin{proof}
See Appendix~\ref{app:packdef}.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:NG_LADDER_IDEM}]
Fix $n\ge 1$. By Lemma~\ref{lem:idempotent-iterates} we have $e^{\circ n}=e$, hence for every $x\in\X$,
\[
e^{\circ n}(x)=e(x).
\]
In particular, the packaged state stabilizes after one step, and any packaged signature depending only
on $e^{\circ n}(x)$ stabilizes after one step as well.
\end{proof}

\subsection{Definability count for a fixed interface}

Let $f:\X\to\Y$ be a deterministic interface observation into a finite set $\Y$.
Define the family of predicates definable from $f$ by
\[
\Def(f)\coloneqq \{g\circ f : \X\to\{0,1\} \mid g:\Y\to\{0,1\}\}.
\]
Only the restriction of $g$ to the image $\im(f)\subseteq \Y$ matters.

\begin{lemma}\label{lem:definability-bijection}
The map
\[
A\subseteq \im(f)\quad\longmapsto\quad \1_A\circ f
\]
is a bijection between $\mathcal P(\im(f))$ and $\Def(f)$. Consequently,
\[
|\Def(f)| = 2^{|\im(f)|}.
\]
\end{lemma}

\begin{proof}
See Appendix~\ref{app:packdef}.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:NG_LADDER_BOUNDED_INTERFACE}]
Assume for contradiction that there exists an infinite strictly increasing sequence
$(h_n)_{n\ge 1}\subseteq \Def(f)$, meaning $h_n(x)\le h_{n+1}(x)$ for all $x\in\X$ and $h_n\neq h_{n+1}$
for each $n$. By Lemma~\ref{lem:definability-bijection}, the set $\Def(f)$ has finite cardinality
$2^{|\im(f)|}$, so it cannot contain infinitely many distinct elements. This contradiction shows that
no such infinite strictly increasing sequence exists.
\end{proof}

\begin{remark}[Extension escape]
Theorem~\ref{thm:NG_LADDER_BOUNDED_INTERFACE} assumes a fixed interface map $f$.
If one allows the interface to vary with the step index (for example by adding coordinates or refining
the lens family so that $|\im(f_n)|$ grows), then the bound $|\Def(f_n)|=2^{|\im(f_n)|}$ can increase and longer
refinement chains become possible. Such interface expansion is outside the scope of the bounded-interface front.
\end{remark}
